### 2017-11-28 paper/sections/2_parsplice-keyspace-analysis.tex
paper: addresses #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-keyspace.png}\\
  \caption{The keyspace size is small but must satisfy many reads as workers
  calculate new segments. Memory usage scales linearly, so It is likely that we will need
  more than one node to manage segment coordinates when we scale the system or jobs up.
  \label{fig:methodology-keyspace}}
\end{figure}

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/motivation-regimes.png}\\
  \caption{The key activity for ParSplice using two different growth
rates.  The line shows the rate that EOM minima values are retrieved from the
key-value store (\(y1\) axis) and the points along the bottom show the number
of keys accessed in a 1 second sliding window (\(y2\) axis).\label{fig:motivation-regimes}}
\end{figure}

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-keys.png}\\
  \caption{The keyspace imbalance is due to workers generating deep
  trajectories and reading the same coordinates. Over time, the accesses get
  dispersed across different coordinates resulting in some keys being more
  popular than others.\label{fig:methodology-keys}}
\end{figure}

>>>>

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-keyspace.png}\\
  \caption{The keyspace is small but must satisfy many reads as workers
  calculate segments. Memory usage scales linearly, so it is likely that we will need
  more than one node to manage segment coordinates when we scale the system or jobs up.
  \label{fig:methodology-keyspace}}
\end{figure}

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/motivation-regimes.png}\\
  \caption{Key activity for ParSplice starts with many reads to a small set of
keys and progresses to less reads to a larger set of keys.  The line shows the
rate that EOM minima values are retrieved from the key-value store (\(y1\)
axis) and the points along the bottom show the number of keys accessed in a 1
second sliding window (\(y2\) axis). Despite having different growth rates
(\(\Delta\)), the structure and behavior of the key activities are similar.
\label{fig:motivation-regimes}}
\end{figure}

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-keys.png}\\
  \caption{ Over time, tasks start to access a larger set of keys resulting in
some keys being more popular than others.  Despite different growth rates
(\(\Delta\)), the spatial locality of key accesses is similar between the two
runs.  ({\it e.g.}, some keys are still read 5 times as many times others).
\label{fig:methodology-keys}}
\end{figure}

### 2017-11-28 paper/sections/3_methodology.tex
paper: addresses #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[h]
\footnotesize
\begin{minted}{lua}
d = timeseries()       -- data (d) from storage system
for i=1,d:size() do    -- iterate over timeseries
  ts, value = d:get(i) -- index into timeseries 
  if value == 'mydirectory' then
    count = count + 1
  end
end
\end{minted}
\end{figure}

>>>>

\begin{figure}[h]
\footnotesize
\begin{minted}{lua}
d = timeseries()       -- d(ata) from storage system
for i=1,d:size() do    -- iterate over timeseries
  ts, value = d:get(i) -- index into timeseries 
  if value == 'mydirectory' then
    count = count + 1
  end
end
\end{minted}
\end{figure}

### 2017-11-28 paper/sections/4_dynamic-policies.tex
paper: addresses #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
\caption{Policy performance/utilization shows the trade-offs of different sized caches
(\(x\) axis).  ``None" is ParSplice unmodified, ``Fixed Sized Cache" evicts
keys using LRU, and ``Multi-Policy Cache" switches to fixed sized cache after
absorbing the workload's initial burstiness.  \label{fig:methodology-tradeoff}}
\end{figure}

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``No Cache Management" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload), and
``Dynamic Policy" (sizes cache according to key access patterns). The ``Dynamic
Policy" saves the most memory without sacrificing performance.
\label{fig:memory-vs-time}}
\end{figure}%

@@

	\caption{Performance/Utilization for dynamically sized cache (DSCache)
policy. With negligible performance degradation, DSCache adjusts to different
\(\Delta\)'s and saves 3\(\times\) as much memory in the best case.
\label{fig:dscache-vs-none}}

>>>>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
\caption{Policy performance/utilization shows the trade-offs of different sized
caches (\(x\) axis).  ``None" is ParSplice unmodified, ``Fixed Sized Cache"
evicts keys using LRU, and ``Multi-Policy Cache" switches to fixed sized cache
after absorbing the workload's initial burstiness. This parameter sweep
identifies the ``Multi-Policy Cache" of 1K keys as the best solution but this
only works for this system setup and initial configurations.
 \label{fig:methodology-tradeoff}}
\end{figure}

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``No Cache Management" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload), and
``Dynamic Policy" (sizes cache according to key access patterns). The dynamic
policies saves the most memory without sacrificing performance.
\label{fig:memory-vs-time}}
\end{figure}%

@@

	\caption{The performance/utilization for the dynamically sized cache (DSCache)
policy. With negligible performance degradation, DSCache adjusts to different initial configurations
(\(\Delta\)'s) and saves 3\(\times\) as much memory in the best case.
\label{fig:dscache-vs-none}}
